Structuring College Access

### 2025-04-10 index.qmd
un-comment out the empirics from the presentation
adding capabilities to slides

---
title: 'Structuring College Access'
subtitle: 'The Market Segment Model and College Board Geomarkets'
author: ['Ozan Jaquette', 'Karina Salazar', 'Crystal Han']
institute: ['UCLA', 'University of Arizona', 'Stanford University']
bibliography: ./assets/bib/cb_geomarket_bib.bib
format:
  revealjs: 
    theme: [default, ./assets/css/custom.scss]
    controls: true
    controls-layout: bottom-right
    controls-tutorial: true
    transition: slide
    background-transition: fade
    auto-stretch: false
    slide-level: 3
    menu:
      titleSelector: 'h1, h2, .slide:not(.hide) h3'
      useTextContentForMissingTitles: false
      hideMissingTitles: true
    template-partials:
      - ./assets/html/title-slide.html
include-in-header: ./assets/html/header.html
---

@@

__Sorting students into colleges, perspectives from sociology:__

- Status attainment model [e.g., @RN915]
- Cultural capital model [e.g., @RN1228]
<!-- - "Schools as sorting machines" [@RN4873] -->
- Enrollment management behavior of colleges [e.g., @RN3519]

__Sociology misses an important mechanism of social reproduction:__

- Third-party vendors/products sort students on behalf of colleges
- Recommendations based on historical snapshots of student demand

__"Geomarkets" are an input in two College Board recruiting products:__

- Student Search Service (est. 1972); Enrollment Planning Service (est. 1984)

@@

1. Enrollment management: Background \& scholarship
1. Empirical case and theory
1. Methods
1. Results
1. Discussion
    - Creating a "knowledge infrastructure" [@RN5025] to study the role of private firms and private equity funding in education

@@

- Visit rich, mostly White public schools [@RN4758]
- Disproportionate visits to private schools [@RN5023]
- "Recruitment redlining": circuitous avoidance of Black and Latinx communities along visit paths [@RN4759] [INSERT CLICKABLE IMAGE OF LA MAP]

___Recruiting not a practice wholly done by colleges...___

- Data vendors and consultancies help colleges find students

@@

>>>>

---
title: 'Structuring College Access'
subtitle: 'The Market Segment Model and College Board Geomarkets'
author: ['Ozan Jaquette', 'Karina Salazar', 'Crystal Han']
institute: ['UCLA', 'University of Arizona', 'Stanford University']
bibliography: ./assets/bib/cb_geomarket_bib.bib
format:
  revealjs:
    revealjs-plugins: [multimodal]   # ← correct key
    theme: [default, ./assets/css/custom.scss]
    controls: true
    controls-layout: bottom-right
    controls-tutorial: true
    transition: slide
    background-transition: fade
    auto-stretch: false
    slide-level: 3
    menu:
      titleSelector: 'h1, h2, .slide:not(.hide) h3'
      useTextContentForMissingTitles: false
      hideMissingTitles: true
    template-partials:
      - ./assets/html/title-slide.html
include-in-header: ./assets/html/header.html
---

@@

__"Geomarkets" carve states and metro areas into smaller geographic regions__

- Geomarkets are an input in two College Board recruiting products:
  - Student Search Service (est. 1972); Enrollment Planning Service (est. 1984)

__Perspectives from sociology on sorting students into colleges:__

- Status attainment model [e.g., @RN915]
- Cultural capital model [e.g., @RN1228]
- Enrollment management behavior of colleges [e.g., @RN3519]
- Sociology ignores third-party products that sort students on behalf of colleges
  - Designed to amplify historic inequality in student demand

<!-- 
__Sociology misses an important mechanism of social reproduction:__

- Third-party vendors/products sort students on behalf of colleges
  - Amplify past structural inequality in student demand
 -->

@@

1. <span style="color:blue">Enrollment management: Background & scholarship</span>  
1. <span style="color:red">Empirical case and theory</span>  
1. <span style="color:red">Methods</span>  
1. <span style="color:red">Results</span>  
1. <span style="color:blue">Discussion<br>– Creating a "knowledge infrastructure" [@RN5025] to study the role of private firms and private equity funding in education</span>

@@

- Visit rich, mostly White public schools [@RN4758]
- Disproportionate visits to private schools [@RN5023]
- "Recruitment redlining": circuitous avoidance of Black and Latinx communities along visit paths [@RN4759] ([LA map](#){data-modal-type="image" data-modal-url="assets/images/recruitment_redlining_map.jpg"})

___But recruiting process not wholly done by colleges...___

- Third-party vendors and consultancies help colleges find and recruit students
<!-- [LA map](#){data-modal-type="image" data-modal-url="assets/images/chicago_geomarkets.png"} -->

@@

- Filters used by public research universities
- [Link](#){data-modal-type="image" data-modal-url="assets/images/research_univ_list_filters.png"}
